Software Ticket Quality

### 2017-11-26 proposal/mprop.tex
Add structured papers in the issue quality section

@@

\textbf{Modeling Bug Report Quality}\cite{hooimeijer2007modeling}
\begin{itemize}
  \item \textbf{What were the goals?}
    The authors' goal is to present a model that would determine if a bug
    report will be triaged in a given amount of time. Moreover, they are 
    trying to propose features that could help composing a good quality
    bug report.
  \item \textbf{What was the method?}
    They run an analysis on over 27000 bug reports from the Mozilla Firefox
    project, selecting a couple of surface features that could be applied:
      \begin{itemize}
        \item self-reported severity;
        \item readability;
        \item daily load (i.e.\ total number of bug reports that need to be
          dealt with at that point in time);
        \item submitter reputation;
        \item changes over time.
      \end{itemize}
    Afterwards, they ran 4 experiments (i.e.\ validate the assumptions, find
    how much post-submission data is necessary, find the optimal resolved by
    cutoff, evaluate the hypothetical benefit) and analyzed the results to
    see if their model would be beneficial.
  \item \textbf{What did they learn?}
    They found out that linear model, even a simple one, can have 
    better-than-chance predictive power. Also, they came to the conclusion that 
    attachment and comment counts are really valuable for triaging the bug faster,
    compared to, for example, patch count. Moreover, the readability of a bug is
    important as it proved to influence the duration of the triaging process. 
  \item \textbf{Relevance to our work}: the authors' goal was quite similar to ours
    as they are trying to find out which features make for a good quality bug 
    report. Moreover, they are also using programmatic analysis instead of
    interviews with developers to produce the results, which is the same approach
    we are aiming for in our research.
\end{itemize}

@@

\textbf{What makes a good bug report}\cite{bettenburg2008makes}:
\begin{itemize}
  \item \textbf{What were the goals?}
  The main goal of the paper was to investigate the \textbf{quality of bug reports} from a developer's
  point of view, based on the typical information found in such a report (e.g.\ stack traces, screenshots).
\item \textbf{What was the method?}
  The authors conducted a massive survey with over 450 respondents. The survey was online and it targeted
  developers from Mozilla, Apache and Eclipse.
\item \textbf{What did they learn?}
  The main conclusion of this research paper was that well written bug reports will more likely get the 
  attention of the developers. Thus, including steps to reproduce the bugs or stack traces proved to increase
  the quality of the bug report. Also, an important achievement reached by the authors was the development of
  a prototype tool called Cuezilla that could estimate, with an accuracy rate of 31\-48\%, the quality of a bug
  report.
\item \textbf{Relevance to our work}: it is relevant to our research in that it provides valuable insight into 
  what makes for a good bug report based on actual professionals' opinions.
\end{itemize}

>>>>

Issue quality is the main topic of this literature review as it revolves around
software tickets and what are the characteristics of a well-written and 
informative bug report, how efficient are bug tracking systems, what defines
an efficient bug triaging process etc.

The first and most important sub-topic of issue quality, which is the one
we will address in our own research as well, is the quality of bug reports.
There are several authors that have tried to defined what makes for a good bug
report and what components actually improve the overall quality.

\citet{bettenburg2008makes} have tried, through their work, to analyze what 
makes for a good bug report through qualitative analysis. They interviewed over
450 developers and asked them what are the most important features for them in
a bug report that help them solve the issue quicker. They reached the conclusion 
that stack traces and steps to reproduce increased the quality of a bug report 
the most, followed by well-written, grammar error free summaries and 
descriptions. Last but not least, they also created a tool called CueZilla that 
could with an accuracy rate between 31 and 48\% predict the quality of a bug 
report.

Strengthening the argument that readability matters considerably in bug report 
quality is the work of \citet{hooimeijer2007modeling}. They ran an analysis over
27000 bug reports from the Mozilla Firefox project, looking at self-reported 
severity, readability, daily load, submitter reputation and changes over time. 
After running the evaluation, they not only found out about the importance of
readability in bug reports, but also that attachment and comment counts are 
valuable for faster triaging and that patch count, for example, does not
contribute in the same manner as the previous two.

@@

@@
